HPC--101\\Onboarding

### 2025-03-14 hpc_101/sections/01_intro.tex
rename to ITS-RCI

  \begin{block}{Online documents \& FAQ}
    Users are encouraged to look through the online documentation \& User Guide prior to contacting ITS-CI directly.  Many questions we receive are repeat questions and we try to capture them in our User Guide.~\\
		\begin{itemize}
		\item \href{http://datascience.hawaii.edu/hpc/}{Information \& policies}
		\item \href{http://go.hawaii.edu/ex2}{Resource Documentation \& User Guide}
		\item \href{http://go.hawaii.edu/3A8}{Video Tutorials}
		\end{itemize}
  \end{block}
  \begin{block}{Contact Information}
    If your question is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu

>>>>

  \begin{block}{Online documents \& FAQ}
    Users are encouraged to look through the online documentation \& User Guide prior to contacting ITS-RCI directly.  Many questions we receive are repeat questions and we try to capture them in our User Guide.~\\
		\begin{itemize}
		\item \href{http://datascience.hawaii.edu/hpc/}{Information \& policies}
		\item \href{http://go.hawaii.edu/ex2}{Resource Documentation \& User Guide}
		\item \href{http://go.hawaii.edu/3A8}{Video Tutorials}
		\end{itemize}
  \end{block}
  \begin{block}{Contact Information}
    If your question is not answered in our online documentation, please contact us at: UH-HPC-Help@lists.hawaii.edu
